Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-11 paper.tex
Be (somewhat) more explicit about parametricity
Reviewer A:

  Vous parlez de paramétricité à plusieurs endroit. Mais je n'ai pas
  vraiment compris ce que vous faites avec? Est-ce que vous prouvez
  des lemmes de paramétricités pour vos fonctions? Peut-être en
  utilisant un plugin (je sais que des plugins pour prouver la
  paramétricité de fonctions polymorphes automatiquement, mais je n'en
  sais pas l'état). C'est un point qui mériterait d'être éclairci,
  probablement.

The relational invariant will then naturally and compositionally
percolate through the various layers of the ciphers. We can then read
off the bitsliced code from the bitsliced types and relational
invariant. A single round of the cipher becomes:
%
\coqfrom{Skinny/Bitslice}{round}

>>>>

The relational invariant will then naturally and compositionally
percolate through the various layers of the ciphers, following the parametricity interpretation of types~\citep{lasson:param}. We can then read
off the bitsliced code from the bitsliced types and relational
invariant. A single round of the cipher becomes:
%
\coqfrom{Skinny/Bitslice}{round}
